### 2014-10-30 transactions.tex
Edits
Transactions. Minor edit

\noindent \begin{minipage}[t]{0.5\columnwidth}
\begin{codehaskell}
save :: Quelea ()
save amt =
  x <- $(chkTxn psi1)
  atomically x $ do
    b <- withdraw c amt
    when b $ deposit s amt
\end{codehaskell}
\end{minipage}
\begin{minipage}[t]{0.5\columnwidth}
\begin{codehaskell}
totalBalance :: Quelea Int
totalBalance =
  x <- $(chkTxn psi2)
  atomically x $ do
    b1 <- getBalance s
    b2 <- getBalance s
    return b1 + b2
\end{codehaskell}
\end{minipage}

\noindent In the above code example, the operations on bank account are simply
wrappers around the store interface. For example,

\begin{codehaskell}
withdraw :: Key -> Int -> Quelea Bool
withdraw k amt = invoke k Withdraw amt
\end{codehaskell}

>>>>

\noindent \begin{minipage}[t]{0.5\columnwidth}
\begin{codehaskell}
save amt =
  x <- $(classify psi1)
  atomically x $ do
    b <- withdraw c amt
    when b $ deposit s amt
\end{codehaskell}
\end{minipage}
\begin{minipage}[t]{0.5\columnwidth}
\begin{codehaskell}
totalBalance =
  x <- $(classify psi2)
  atomically x $ do
    b1 <- getBalance s
    b2 <- getBalance s
    return b1 + b2
\end{codehaskell}
\end{minipage}
